Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory

### 2016-06-08 intro.tex
excitation - additional sentences
add exchange ICD agin

Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
 which the originally excited site is neutralized by the decay.
% and `exchange ICD' for charge transfer contributions to the 
% normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization play a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong
(covalent or metallic) bonding, it is impossible to make a
distinction between ICD and Auger decay.\cite{hergenhahn_review}

>>>>

Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
 which the originally excited site is neutralized by the decay.
 and `exchange ICD' for charge transfer contributions to the 
 normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization play a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong
(covalent or metallic) bonding, it is impossible to make a
distinction between ICD and Auger decay.\cite{hergenhahn_review}
